---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

<!-- badges: start -->
[![Travis build status](https://travis-ci.com/jgbond/fars-pack.svg?branch=master)](https://travis-ci.com/jgbond/fars-pack)
<!-- badges: end -->

# FARS

The FARS package provides two functions to make analysis of FARS datasets easier. One function, fars_summarize_years, returns a Tibble of FARS data showing total events in each month and year. The other, fars_map_state, returns a graphical map of a specified state with locations of all FARS events in the specified year.

FARS data is from the US National Highway Traffic Safety Administration's Fatality Analysis Reporting System, which is a nationwide census providing the American public yearly data regarding fatal injuries suffered in motor vehicle traffic crashes. The data provided in this package only covers the years 2013-2015.

## Accessing the package
```{r, eval = FALSE}
library(devtools)
install_github("jgbond/fars")
library(fars)
```

## Examples

This is an example of how to use the fars_summarize_years() function in action. It takes a list of years as the input. Years generally should be in 4-digit format. Outputs are not displayed in the readme.

```{r, eval = FALSE}
fars_summarize_years(list(2013,2014,2015))
```

This is an example of the fars_map_state() function in action. As inputs it takes a numerical code for a U.S. state and a 4-digit year. Not all states have data for all years. Outputs are not displayed in the readme.

```{r, eval = FALSE}
fars_map_state(5, 2014)
```

