---
title: "fars_vignette"
author: "Jeff B."
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{fars_vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Overview of this package

The FARS package provides two functions to make analysis of FARS datasets easier. One function, fars_summarize_years, returns a Tibble of FARS data showing total events in each month and year. The other, fars_map_state, returns a graphical map of a specified state with locations of all FARS events in the specified year.

FARS data is from the US National Highway Traffic Safety Administration's Fatality Analysis Reporting System, which is a nationwide census providing the American public yearly data regarding fatal injuries suffered in motor vehicle traffic crashes. The data provided in this package only covers the years 2013-2015.

## Accessing the package
```{r eval = FALSE}
library(devtools)
install_github("jgbond/fars")
library(fars)
```

## Examples

This is an example of how to use the fars_summarize_years() function in action. It takes a list of years as the input. Years generally should be in 4-digit format. Outputs are not displayed in the vignette.

```{r, eval=FALSE}
fars_summarize_years(list(2013,2014,2015))
```

This is an example of the fars_map_state() function in action. As inputs it takes a numerical code for a U.S. state and a 4-digit year. Not all states have data for all years. Outputs are not displayed in the vignette.

```{r, eval=FALSE}
fars_map_state(5, 2014)
```
